Optimized average-based embeddings for word sense disambiguation problem

### 2019-02-11 paper/main.tex
Improve intro to experiments and move limitations

\section{Dataset}
\label{dataset}
For the purpose of testing word embeddings as a method to differentiate between different meanings, we gathered examples for 6 ambiguous words, 4-7 meanings each (28 meanings in total).
Ambiguous word together with its meaning constitues a \textit{keyword}, which we use as a separate class when identyfing the closest meaning given some context.
All keywords can be seen on Figure 1.

@@

\section{Our method}
\subsection{Keyword embedding}
\textit{Keyword} is a sequence of words that lets us disambiguate between different meanings of the same ambiguous word, e.g. "tree forest" that represents a tree as a plant and "tree structure" which represents tree as a mathematical structure.

@@

\subsection{Context embedding}
\textit{Context} is a sequence of words that contains an ambiguous word within, usually in the middle.
It is parametrized by context length \(l\), which specifies how many of words from both side of the ambiguous word in question were taken into consideration.

@@

\subsection{Optimization}
As a baseline, we use keyword and context embeddings described above to find the closest keyword given some context, using cosine distance as a metric.
To optimize this system, we use texts from the training set to improve the quality of keyword embeddings.
For each training example, we shift the correct keyword embedding by a factor of \(\alpha\) in the direction of context embedding, which describes said keyword.

@@

\section{Experiments}
\subsection{Assumptions}
Since our goal is to check how embedding approach works for WSD problem, we use pretrained embedding model from spaCy - en\_vectors\_web\_lg, 300-dimensional word vectors trained on Common Crawl with GloVe.\cite{spacymodel}.
Due to high impact of training data order on test results, we take the average score of 30 runs (with random order of training data) for each optimization experiment.
The best configuration of each experiment is taken as a baseline for the next experiment.
The goal of these experiments is to show how each of parameters influences on model's accuracy after training.

We are aware that our method has some limitations.
Firstly, it may be impossible to achieve optimal solution as we can move only keywords, we leave contexts fixed in the multidimensional space and it is possible that contexts for specific keyword overlap on contexts for other keyword. Hence, top 3 accuracy may be much better than top 1 accuracy.
Another limitation is that averaged context embedding may be ambiguous, since it is just average, two different contexts may be represented by same vector.
\subsection{Baseline}
First of experiments is to check how out-of-the-box model works without extra optimizations. We perform tests with different context lengths, as a score we choose top 1 and top 3 accuracy. Results are shown in the Fig. \ref{fig:baseline}.

@@

\section{Conclusion and future work}

>>>>

\section{Dataset}
\label{sec:dataset}
For the purpose of testing word embeddings as a method to differentiate between different meanings, we gathered examples for 6 ambiguous words, 4-7 meanings each (28 meanings in total).
Ambiguous word together with its meaning constitues a \textit{keyword}, which we use as a separate class when identyfing the closest meaning given some context.
All keywords can be seen on Figure 1.

@@

\section{Our method}
\subsection{Keyword embedding}
\label{sec:kw_embed}
\textit{Keyword} is a sequence of words that lets us disambiguate between different meanings of the same ambiguous word, e.g. "tree forest" that represents a tree as a plant and "tree structure" which represents tree as a mathematical structure.

@@

\subsection{Context embedding}
\label{sec:ctx_embed}
\textit{Context} is a sequence of words that contains an ambiguous word within, usually in the middle.
It is parametrized by context length \(l\), which specifies how many of words from both side of the ambiguous word in question were taken into consideration.

@@

\subsection{Optimization}
\label{sec:optimization}
As a baseline, we use keyword and context embeddings described above to find the closest keyword given some context, using cosine distance as a metric.
To optimize this system, we use texts from the training set to improve the quality of keyword embeddings.
For each training example, we shift the correct keyword embedding by a factor of \(\alpha\) in the direction of context embedding, which describes said keyword.

@@

\subsection{Limitations}
We are aware that our method has some limitations.
First of all, it may be impossible to achieve the optimal solution, as we can only optimize keyword embeddings, leaving context embeddings fixed in the multidimensional space.
Therefore, it is possible that contexts for specific keyword overlap on contexts for other keyword.

Secondly, the average context embedding may be ambiguous, with a high possibility of two different context being mapped to a similar point in space, especially for longer context legths.
In future work (\ref{sec:conclusion}), we suggest experimenting with different sequence embedding techniques, that might be better suited for this purpose than a flat average.

\section{Experiments}
The goal of following experiments is to check how embedding approach (\ref{sec:kw_embed}, \ref{sec:ctx_embed}) works for the dataset we collected (\ref{sec:dataset}), both out-of-the-box (baseline) and after applying optimization techniques (\ref{sec:optimization}).
We use a pretrained embedding model from spaCy - \textit{en\_vectors\_web\_lg}, which contains 300-dimensional word vectors trained on Common Crawl with GloVe\cite{spacymodel}.

Due to the high impact of training data order on test results, we take the average score of 30 runs (each with a random order of training data) for each optimization experiment.
The best configuration of each experiment is taken as a baseline for the next experiment.
The goal of these experiments is to show how each of parameters influences on model's accuracy after training.

We compare our results with two metrics: top-1 accuracy, where we are only interested, if the correct keyword is the closest one to a specific context describing it, and top-3 accuracy, where we check if we are in the closest three keywords.

\subsection{Baseline}
First of experiments is to check how out-of-the-box model works without extra optimizations. We perform tests with different context lengths, as a score we choose top 1 and top 3 accuracy. Results are shown in the Fig. \ref{fig:baseline}.

@@

\section{Conclusion and future work}
\label{sec:conclusion}
